---
title: "Getting Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The `fleetbr` package contains a single dataset of the registered motor vehicles in Brazil by state and mode of transportation from 2011 to 2021, provided in `tibble` format for integration with the `tidyverse` packages. The date is acquired from the open data sources of the Brazilian Ministry of Transport.

## Instalation

You can install the development version of `fleetbr` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jotasaraiva/fleetbr")
```

## Example

Afterwards, the package can be loaded along with the `dplyr`, `ggplot2` and `lubridate` packages for filtering and plotting a subset of the data:  

```{r setup, warning=FALSE, message=FALSE}
library(fleetbr)
library(dplyr)
library(ggplot2)
library(lubridate)
```

In this example, a time series of the data from the state of São Paulo is displayed:

```{r, warning=FALSE}
fleetbr |> 
  filter(uf == "SP") |> 
  mutate(
    dates = ym(paste0(ano,"-",mes))
  ) |> 
  ggplot(aes(dates,frota, color = modal)) + 
    geom_line(linewidth = 1)
```


